General writeup

### 2017-11-25 Latex/general_writeup.tex
New Nice specification
I run the following specification:

TFP (log)
Real SP500 (log)
MichIndex (level)
IT Investment (log)
Real Cons (log)
Relative Prices (log-diff)

One lag, zero restriction in 8 quarters.

The result is super nice. In my opinion is even better than the one we showed Ryan.

I had the result to the Latex file you made.

%%%%%%%%
%two lags instead of one (back to LR hor = 8)

%%%%%%%%
% adding stock prices

>>>>

%%%%%%%%
%two lags instead of one (back to LR hor = 8), adding real stock prices 500, removing GDP, with relative price
\newpage
	\subsection{Capital prices LR horizon 8}
	\noindent one lag, LR hor = 8, adding real stock prices 500, removing GDP, with relative price

	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_25-Nov-2017_11_39_14}

	\begin{figure}[h!]
\centering
\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_25-Nov-2017_11_30_49}} \hspace{.2in%
} 
\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_25-Nov-2017_11_30_52}}
\end{figure}

%%%%%%%%
%one lag (back to LR hor = 8)

%%%%%%%%
% adding real SP
